EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-05-04 draft.tex
revise cloud deployment, refs #6

\subsection{Deploying to a Cloud Provider}

% This is only an idea of the section
% 
Several options:
    A virtual machine with a container-optimized operating system, for example,
     Google Compute Engine VMs, or Amazon EC2.  We still need to provision the
      virtual machine and run docker-compose commands as we would do in a local 
      workstation.

@@

As a proof-of-concept, we deployed the EvoSwarm application in Amazon Elastic
Container Service (ECS).  Because it needs fewer changes in configuration, 
and it is has a lower cost than a Kubernetes alternative.

@@

Using the ECS CLI, we can provision a cluster with a configuration file
specifying the computing resources needed. Multicontainer applications are
deployed to ECS as tasks, and a single cluster can run multiple tasks in
parallel. When using the Fargate service as a backend, tasks are limited to a
maximum of 10 containers.

>>>>

\subsection{Deploying to a cloud provider}

% This is only an idea of the section
%
% First you have to say that cloud is a way of describing deployment to any kind of infrastructure in a reproducible way, and it needn't be in the cloud proper, it can be deployed to anything, that's precisely the thing. 
Several options:
    A virtual machine with a container-optimized operating system, for example,
     Google Compute Engine VMs, or Amazon EC2.  We still need to provision the
      virtual machine and run docker-compose commands as we would do in a local 
      workstation. % Remember that Salza et al. used CoreOS, which is optimized for containers - JJ

@@

    % This is the second option. The first option was already tested, right? - JJ
As a proof-of-concept, we deployed the EvoSwarm application in Amazon Elastic
Container Service (ECS),  since it needs fewer changes in configuration (from deploying it locally using docker-compose)
and it is has a lower cost than a Kubernetes alternative.

@@

Using the ECS CLI, we can provision a cluster with a configuration file
specifying the computing resources needed. Multicontainer applications are
% Maybe an example - JJ
deployed to ECS as tasks, and a single cluster can run multiple tasks in
parallel. When using the Fargate service as a backend, tasks are limited to a
maximum of 10 containers.
